Syntax and Semantics of Abstract Binding Trees

### 2015-12-06 paper.tex
Explain "presupposition"

Let the judgment $\IsAbt{\Theta}{\Upsilon}{\Gamma}{M}{\tau}$ presuppose
$\IsMetaCtx{\Theta}$, $\IsSymCtx\Upsilon$, $\IsVarCtx\Gamma$ and
$\IsSort{\tau}$, meaning that $M$ is an abstract binding tree of sort $s$, with
metavariables in $\Theta$, parameters in $\Upsilon$, and variables in $\Gamma$.
Let the judgment $\IsBTm{\Theta}{\Upsilon}{\Gamma}{E}{v}$ presuppose
$\IsValence{v}$. Then, the syntax of abstract binding trees is inductively
defined in four rules:

>>>>

Let the judgment $\IsAbt{\Theta}{\Upsilon}{\Gamma}{M}{\tau}$ presuppose
\footnote{
  In the \emph{judgmental method}, as pioneered by Per Martin-L\"of, a form of
  judgment is propounded first by specifying its range of significance (i.e.\
  the circumstances under which it shall have a meaning), and then, a meaning
  explanation (definition) for the judgment is given. The range of significance
  of a judgment is called its \emph{presupposition}, and the meaning of the
  judgment may proceed by induction on the evidence that the presupposition
  obtains. See \cite{schroeder-heister:1987} for a more detailed explanation of
  presuppositions and the judgmental method.
}
$\IsMetaCtx{\Theta}$, $\IsSymCtx\Upsilon$, $\IsVarCtx\Gamma$ and
$\IsSort{\tau}$, meaning that $M$ is an abstract binding tree of sort $s$, with
metavariables in $\Theta$, parameters in $\Upsilon$, and variables in $\Gamma$.
Let the judgment $\IsBTm{\Theta}{\Upsilon}{\Gamma}{E}{v}$ presuppose
$\IsValence{v}$. Then, the syntax of abstract binding trees is inductively
defined in four rules:
